Multi-task Mutual Learning for Vehicle Re-Identification

### 2019-04-24 paper.tex
change abstract

%%%%%%%%% ABSTRACT
\begin{abstract}
  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract  abstract
\end{abstract}

@@

{\small
\bibliographystyle{cvpr2019AuthorKit/latex/ieee_fullname}
\bibliography{../Bibliography/reid_bibliography.bib}
}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}

\end{abstract}

@@

{\small
\bibliographystyle{cvpr2019AuthorKit/latex/ieee_fullname}
\bibliography{bibliography.bib}
}
